### 2015-08-28 fundamentals/conclusion.tex
conclusion cleanup.

The \Cyclus nuclear fuel cycle framework presents a more generic and flexible
alternative to existing fuel cycle simulators. Where previous nuclear fuel
cycle simulators have had limited distribution, constrained simulation
capabilities, and restricted customizability, \Cyclus emphasizes an open
strategy for access and development.  This open strategy not only improves
accessibility, but also enables transparency and community oversight.

The object-oriented \gls{ABM} simulation paradigm ensures more generic
simulation capability. It allows \Cyclus to address common analyses in a more
flexible fashion and enables analyses that are impossible with system dynamics
simulators.

Similarly, the fidelity-agnostic, modular \Cyclus architecture facilitates simulations
at every level of detail. Simulations relying on arbitrarily complex isotopic
compositions are possible in \Cyclus, as are simulations not employing any
physics at all. To support this, the \Cycamore library provides models 
employing basic physics for core fuel cycle facilities and extension libraries 
from the community more support detailed simulations. Indeed, agents of such 
varying fidelity can even exist in the same simulation. Researchers no longer 
need to reinvent the underlying simulator framework in order to model a simulation 
focused on the aspects of the fuel cycle relevant to their research.

>>>>

The \Cyclus nuclear fuel cycle framework presents a more generic and flexible
alternative to existing fuel cycle simulators. Where previous nuclear fuel
cycle simulators have had limited distribution, constrained simulation
capabilities, and restricted customizability, \Cyclus emphasizes an open
strategy for access and development.  This open strategy not only improves
accessibility, but also enables transparency and community oversight. 
Furthermore, the object-oriented \gls{ABM} simulation paradigm ensures more generic
simulation capability. It allows \Cyclus to address common analyses in a more
flexible fashion and enables analyses that are impossible with system dynamics
simulators.

Similarly, the fidelity-agnostic, modular \Cyclus architecture facilitates simulations
at every level of detail. Simulations relying on arbitrarily complex isotopic
compositions are possible in \Cyclus, as are simulations not employing any
physics at all. Physics is introduced through optional system-wide radioactive 
decay of materials and through the use of physics-enabled facility libraries.  
To support calculation of physical processes in nuclear facilities, the 
\Cycamore library provides models employing basic physics for core fuel cycle 
facilities and extension libraries from the community support more detailed 
simulations. Indeed, agents of such varying fidelity can even exist in the same 
simulation. Researchers no longer need to reinvent the underlying simulator 
framework in order to model a simulation focused on the aspects of the fuel 
cycle relevant to their research.
